### 2018-07-13 doc/plos/text/manuscript.tex
combine sensor plots
The top/bottom subplots are now a single image. I updated the title and
caption of Table 1 and Figure 1.

\begin{table}[!ht]
  \centering
  \caption{{\bf TODO(Table caption.)}}
  \begin{tabular}{|l|l|l|}
    \hline
    {\bf Source} & {\bf Weeks} & {\bf Locations}\\ \thickhline
    GFT & 254 & 62 \\ \hline
    GHT & 402 & 52 \\ \hline
    TWTR & 339 & 71 \\ \hline
    WIKI & 402 & 1 \\ \hline
    CDCP & 276 & 71 \\ \hline
    EPIC & 119 & 15 \\ \hline
    SAR3 & 402 & 75 \\ \hline
    ARCH & 265 & 20 \\ \hline
  \end{tabular}
  \begin{flushleft}
    TODO(Table notes.)
  \end{flushleft}
  \label{table_sensor_breakdown}
\end{table}

\begin{figure}[!h]
  \maybeincludegraphics{sensor_heatmap_top}
  \maybeincludegraphics{sensor_heatmap_bottom}
  \caption{
    {\bf TODO(figure title.)}
    TODO(Figure caption top and bottom.)
  }
  \label{figure_sensor_heatmap}
\end{figure}

>>>>

\begin{table}[!ht]
  \centering
  \caption{{\bf Sensor coverage across time and location.}}
  \begin{tabular}{|l|l|l|}
    \hline
    {\bf Source} & {\bf Weeks} & {\bf Locations}\\ \thickhline
    GFT & 254 & 62 \\ \hline
    GHT & 402 & 52 \\ \hline
    TWTR & 339 & 71 \\ \hline
    WIKI & 402 & 1 \\ \hline
    CDCP & 276 & 71 \\ \hline
    EPIC & 119 & 15 \\ \hline
    SAR3 & 402 & 75 \\ \hline
    ARCH & 265 & 20 \\ \hline
  \end{tabular}
  \label{table_sensor_breakdown}
\end{table}

\begin{figure}[!h]
  \maybeincludegraphics{sensor_heatmap}
  \caption{
    {\bf National sensor readings fitted from eight data sources.}
    Top: Plot of sensor readings and ground truth wILI (black) over time,
    highlighting sensor noise.
    Bottom: Heatmap of sensor readings over time, highlighting sensor
    intermittency.
  }
  \label{figure_sensor_heatmap}
\end{figure}
